---
title: "DOGE Functionality"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DOGE Functionality}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup,echo=FALSE}
library(govScrapeR)
```
This package has two main operations: scraping data from doge.gov, and pulling data queries from fpds.gov. The primary functions for each are `doge_get_data()` and `fpds_get_data()`, respectively. Several convenience functions are provided on top of these two. 

## Getting DOGE Data
As of now, the scraper captures data from doge.gov/savings. It relies on ``rvest` and reads dynamically-generated scripts. The data is then cleaned, and returned in table format. 
```{r,echo=TRUE}

#df <- doge_get_data(verbose=T,saveFile = F)
df <- readRDS("../inst/extdata/DOGE/doge.RDS")
names(df)
```
As of the writing of this vignette, DOGE displayed data on three groups: contracts, grants, and real-estate. Each group continas different table structure, so the data is returned in a named list, comprised of three dataframes. The key columns for reference are `ceiling_value` and `value`. These correspond to "Total Value" and "Savings" tabs on doge.gov/savings.

If desired, you can save data to an .RDS file by flagging `saveFile=TRUE`, and providing a directory location to the `saveDir` parameter. 

## Getting FPDS Data
The `contracts` table has an `fpds_link` column, allowing the user to click through to the relevant entry on fpds.gov. There appear to be inconsistencies. Therefore, to assist in validating published data with government data, you can use `fpds_get_data()` to query the ATOM feed for each contract.
```{r}
f <- fpds_get_data(piid=c("9523ZY21P0045","9531CB24A0009"))
names(f)
```
Two types of contracts are identified in DOGE data: awards and IDV. Information about these, and other variables are available in the FPDS data dictionary: https://www.fpds.gov/downloads/Version_1.5_specs/FPDS_DataDictionary_V1.5.pdf. Because they are structured slightly differently, `fpds_get_data()` will return a named list, with relevant dataframes. 

As a note, to avoid overloading memory, FPDS data is written to a `tempdir()` location, then merged at the end of the function. 

## Updating FPDS Data
The data from doge.gov/savings is periodically updated. When it is, you can use `fpds_get_new()` with the new DOGE data, and an existing FPDS data object to identify and query only the new additions to the DOGE data. This alleviates unnecessarily long queries every time there's a change on doge.gov/savings.



